### 2021-05-31 docs/manuscript/manuscript.tex
Mention most studies focus on single input

However, although several studies have analyzed the properties of GRNs that
process positional information, they have focused on particular natural networks
\cite{Schaerli2014,Jaeger2004}, in synthetic networks
\cite{Basu2005,Reinitz1995,Schaerli2018}, or have constrained the design of the
GRNs \cite{Elowitz2000}.

>>>>

However, although several studies have analyzed the properties of GRNs that
process positional information, they have focused on particular natural networks
\cite{Schaerli2014,Jaeger2004}, in synthetic networks
\cite{Basu2005,Reinitz1995,Schaerli2018,Elowitz2000}, or have constrained the
design of the GRNs to accept an input signal from only one of its nodes, which is
not always biologically realistic as multiple input systems can exist~
\cite{Cotterell2010, munteanu_2014, Schaerli2014}.
